Reading Notes

### 2020-08-18 2pd.tex
fix typo. update library

% With Matt - What intermolecular interactions guide diphenylurea crystal formation
An investigation of the supramolecular interactions which guide crystal self-assembly in diphenylurea transition metal complexes using density functional theory\cite{Millard2019a}. 
% With us - Perspective paper about all things
My contributions to our perspective paper were mostly about my experience joining the lab and trying to reproduce and existing model--something which should be very straightforward in a computational field, but which any computational scientist can attest is not simple\cite{Jankowski2019}. 
 %% frame gixstapose as a tool for reproducible, approachable science
I also presented a tool I've developed, called GIXStapose, at the Scientific Python conference (SciPy2020). %%cite scipy and gixstapose
GIXStapose is an interactive structure viewer alongside its simulated diffraction pattern.
This work had two goals: helping users to see the connections between a structure and it's diffraction pattern and making reproducible figure generation easier.
The first goal is achieved through a graphical user interface (GUI) which allows users to interact with the structure using the mouse and the diffraction pattern is updated automatically.
The second goal is accomplished by allowing all steps of the figure generation process (e.g., positioning the camera, setting the colors and lighting, etc) to be scripted and never \testit{requiring} use of the GUI.

>>>>

% With Matt - What intermolecular interactions guide diphenylurea crystal formation
An investigation of the supramolecular interactions which guide crystal self-assembly in diphenylurea transition metal complexes using density functional theory\cite{Millard2019a}. 
% With us - Perspective paper about all things
My contributions to our perspective paper were mostly about my experience joining the lab and trying to reproduce and existing model--something which should be very straightforward in a computational field, but which any computational scientist can attest is not simple\cite{Jankowski2019}. 
 %% frame gixstapose as a tool for reproducible, approachable science
I also presented a tool I've developed, called GIXStapose, at the Scientific Python conference (SciPy2020). %%cite scipy and gixstapose
GIXStapose is an interactive structure viewer alongside its simulated diffraction pattern.
This work had two goals: helping users to see the connections between a structure and it's diffraction pattern and making reproducible figure generation easier.
The first goal is achieved through a graphical user interface (GUI) which allows users to interact with the structure using the mouse and the diffraction pattern is updated automatically.
The second goal is accomplished by allowing all steps of the figure generation process (e.g., positioning the camera, setting the colors and lighting, etc) to be scripted and never \textit{requiring} use of the GUI.
